Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-10-31 docs/00-manuscripts/mdpi/performance-best-per-learner.tex

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run. For 	exttt{regr.featureless} the Task is no applicable and was therefore removed.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.12 & 19.12 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & - & regr.featureless & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 31.25 & 14.96 \\ 
  6 & HR & XGBoost & Car & 34.07 & 13.57 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run. For 	exttt{regr.featureless} the Task is no applicable and was therefore removed.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.119 & 19.123 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.165 & 15.025 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.165 & 15.025 \\ 
  4 & - & regr.featureless & No Filter & 31.165 & 15.025 \\ 
  5 & HR & RF & Relief & 31.246 & 14.956 \\ 
  6 & HR & XGBoost & Car & 34.071 & 13.571 \\ 
   \hline
\end{tabular}
}
\end{table}
